### 2021-01-31 博士/毕业论文/ucasthesis/Tex/Chap_globally.tex
删除 vspace 对行距的压缩
完善 globally 一章图片尺寸

\begin{figure}[t]
    \centering
    \includegraphics[width=0.48\textwidth]{Img/globally/visulization.pdf}
    \vspace{-1cm}
    \caption{A comparison of our method with the stage-of-the-art trackers SiamMask \cite{Wang2018SiamMask} and SiamFCv2 \cite{bertinetto2016fully} in challenging situations. The example frames are from the GOT-10k \cite{huang2018got} testing set.
    % Our approach performs better compared to existing approaches.
    }
    \vspace{-0.5cm}
    \label{fig:visulization}
\end{figure}

@@

\textbf{Overall Performance}
We compare our proposed method with 8 trackers including state-of-the-arts, on GOT-10k testing set.
%To reflect the generalization ability, all deep learning based trackers are trained using the GOT-10k training set.
\begin{table}
\centering
\caption{Performance of our algorithm with different components on GOT-10k test set.}
\begin{tabular}{c c c c c}
\bottomrule
ROI head & Motion model & $AO$ & $SR_{0.50}$ & $SR_{0.75}$ \\ 
\hline
          &           & 0.410 & 0.486 & 0.162 \\
\checkmark&           & 0.521 & 0.595 & 0.440 \\
\checkmark&\checkmark & 0.560 & 0.645 & 0.457 \\
\bottomrule
\label{tabel:ablation}
\end{tabular}
%\vspace{-0.8cm}
\end{table}
\begin{table}
\centering
\caption{Comparing the results of our approach against other approaches over the GOT-10k test set. The trackers are ranked by their average overlap (AO) scores.}
\begin{tabular}{l l l l}
\bottomrule
Method   &  $AO$   &  $SR_{0.50}$ & $SR_{0.75}$  \\
\hline
Ours &  $\textbf{0.560}^\textbf{1}$ & $\textbf{0.645}^\textbf{1}$  & $\textbf{0.457}^\textbf{1}$  \\
SiamMask &  0.459&  0.560 &0.205 \\
SiamFCv2 &  0.374&  0.404 &0.144 \\
SiamFC   &  0.348&  0.353 &0.098 \\
GOTURN	 &  0.347&  0.375 &0.124 \\
CCOT	 &  0.325&  0.328 &0.107 \\
ECO	     &  0.316&  0.309 &0.111 \\
CF2	     &  0.315&  0.297 &0.088 \\
MDNet	 &  0.299&  0.303 &0.099 \\
%CFNetc2	 &  0.293&  0.265 &0.087 \\
%ECOhc	 &  0.286&  0.276 &0.096 \\
\bottomrule
\end{tabular}
\label{table:got}
\end{table}
%The success plot of the evaluated trackers is shown in Fig. \ref{fig:ao}.
Compared to the listed approaches, our approach achieves a superior AO of 0.560 (Table \ref{table:got}).
%CSK is a typical DCF-based tracker, which uses a well-established theory of Circulant matrices to derive closed-form solutions for training and detection with several types of kernels. In contrast, our tracker is based on powerful CNNs. As a result, our tracker significantly outperforms CSK with a relative gain of 173.17\% in terms of AO, which suggests the excellence of the CNN framework as well as the effectiveness of GSTP.
%MDNet learns shared layers and multiple branches of domain-specific layers, where domains correspond to individual training sequences and each branch is responsible for binary classification to identify target in each domain. In contrast, our tracker learns a general similarity map by cross-correlation between the feature representations learned for the target template and the search region. Compared with MDNet, the relative improvement of the AO score is 87.29\%, which suggests that the Siamese architecture and the cross-correlation operation are more suitable for the object tracking task.
%SiamMask is one of state-of-the-art trackers. It is a Siamese tracker and takes advantage of very deep networks to extract features. SiamMask utilizes the region proposal subnetwork to predict the location of the target. 
Compared with SiamMask \cite{Wang2018SiamMask}, our two stage tracker is designed based on the global perception mechanism to reducing cumulative inaccuracies. The motion model suppresses distractors and improves the tracking robustness. As a result, our tracker outperforms SiamMask by relative 22.00\% in terms of AO, which highlights the importance of the proposed tracker and the motion model.

@@

\begin{figure}[htb]
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.2cm]{Img/globally/UAV20L/quality_plot_overlap_OPE_AUC.png}}
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.2cm]{Img/globally/UAV20L/quality_plot_error_OPE_threshold.png}}
\end{minipage}
%
\vspace{-0.5cm}
\caption{Success and precision plots on UAV20L dataset.}
\label{fig:uav20l}
%
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\textwidth]{Img/globally/visulization.pdf}
    \caption{A comparison of our method with the stage-of-the-art trackers SiamMask \cite{Wang2018SiamMask} and SiamFCv2 \cite{bertinetto2016fully} in challenging situations. The example frames are from the GOT-10k \cite{huang2018got} testing set.
    % Our approach performs better compared to existing approaches.
    }
    \label{fig:visulization}
\end{figure}

@@

\textbf{Overall Performance}
We compare our proposed method with 8 trackers including state-of-the-arts, on GOT-10k testing set.
%To reflect the generalization ability, all deep learning based trackers are trained using the GOT-10k training set.
\begin{table}
\centering
\caption{Performance of our algorithm with different components on GOT-10k test set.}
\begin{tabular}{c c c c c}
\bottomrule
ROI head & Motion model & $AO$ & $SR_{0.50}$ & $SR_{0.75}$ \\ 
\hline
          &           & 0.410 & 0.486 & 0.162 \\
\checkmark&           & 0.521 & 0.595 & 0.440 \\
\checkmark&\checkmark & 0.560 & 0.645 & 0.457 \\
\bottomrule
\label{tabel:ablation}
\end{tabular}
\end{table}
\begin{table}
\centering
\caption{Comparing the results of our approach against other approaches over the GOT-10k test set. The trackers are ranked by their average overlap (AO) scores.}
\begin{tabular}{l l l l}
\bottomrule
Method   &  $AO$   &  $SR_{0.50}$ & $SR_{0.75}$  \\
\hline
Ours &  $\textbf{0.560}^\textbf{1}$ & $\textbf{0.645}^\textbf{1}$  & $\textbf{0.457}^\textbf{1}$  \\
SiamMask &  0.459&  0.560 &0.205 \\
SiamFCv2 &  0.374&  0.404 &0.144 \\
SiamFC   &  0.348&  0.353 &0.098 \\
GOTURN	 &  0.347&  0.375 &0.124 \\
CCOT	 &  0.325&  0.328 &0.107 \\
ECO	     &  0.316&  0.309 &0.111 \\
CF2	     &  0.315&  0.297 &0.088 \\
MDNet	 &  0.299&  0.303 &0.099 \\
%CFNetc2	 &  0.293&  0.265 &0.087 \\
%ECOhc	 &  0.286&  0.276 &0.096 \\
\bottomrule
\end{tabular}
\label{table:got}
\end{table}
%The success plot of the evaluated trackers is shown in Fig. \ref{fig:ao}.
Compared to the listed approaches, our approach achieves a superior AO of 0.560 (Table \ref{table:got}).
%CSK is a typical DCF-based tracker, which uses a well-established theory of Circulant matrices to derive closed-form solutions for training and detection with several types of kernels. In contrast, our tracker is based on powerful CNNs. As a result, our tracker significantly outperforms CSK with a relative gain of 173.17\% in terms of AO, which suggests the excellence of the CNN framework as well as the effectiveness of GSTP.
%MDNet learns shared layers and multiple branches of domain-specific layers, where domains correspond to individual training sequences and each branch is responsible for binary classification to identify target in each domain. In contrast, our tracker learns a general similarity map by cross-correlation between the feature representations learned for the target template and the search region. Compared with MDNet, the relative improvement of the AO score is 87.29\%, which suggests that the Siamese architecture and the cross-correlation operation are more suitable for the object tracking task.
%SiamMask is one of state-of-the-art trackers. It is a Siamese tracker and takes advantage of very deep networks to extract features. SiamMask utilizes the region proposal subnetwork to predict the location of the target. 
Compared with SiamMask \cite{Wang2018SiamMask}, our two stage tracker is designed based on the global perception mechanism to reducing cumulative inaccuracies. The motion model suppresses distractors and improves the tracking robustness. As a result, our tracker outperforms SiamMask by relative 22.00\% in terms of AO, which highlights the importance of the proposed tracker and the motion model.

@@

\begin{figure}[htb]
\begin{minipage}[b]{0.5\linewidth}
  \centering
  \centerline{\includegraphics[width=1.0\textwidth]{Img/globally/UAV20L/quality_plot_overlap_OPE_AUC.png}}
\end{minipage}
\hfill
\begin{minipage}[b]{0.5\linewidth}
  \centering
  \centerline{\includegraphics[width=1.0\textwidth]{Img/globally/UAV20L/quality_plot_error_OPE_threshold.png}}
\end{minipage}
%
\caption{Success and precision plots on UAV20L dataset.}
\label{fig:uav20l}
%
\end{figure}
